Quantifying the number of *rrn* operons across taxonomic ranks

### 2020-10-07 exploratory/2020-10-05-rrn-copy-number.Rmd
Add line segment to cloud of points to indicate average, closes #29

---
title: "Quantifying the number of *rrn* operons across taxonomic ranks"
author: "Pat Schloss"
date: "10/05/2020"
output:
  github_document:
    html_preview: false
editor_options:
  chunk_output_type: console
---

@@

rank_taxon_rrns %>%
	ggplot(aes(x=rank, y=mean_rrns)) + 
	geom_jitter(width=0.3, alpha=0.3) +
	theme_classic() +
	labs(x=NULL, 
			 y="Mean number of rrn copies per genome",
			 title="There is wide variation at the species level in the number of rrn copies",
			 subtitle="Each point represents a single taxon within that rank, numbers based on\nan average species copy number")
```

>>>>

---
title: "Quantifying the number of *rrn* operons across taxonomic ranks"
author: "Pat Schloss"
date: "10/05/2020"
output:
  github_document:
    html_preview: false
---

@@

mean_of_means <- rank_taxon_rrns %>%
	group_by(rank) %>%
	summarize(mean_mean_rrns = mean(mean_rrns), .groups="drop")

jitter_width <- 0.3
n_ranks <- nrow(mean_of_means)

rank_taxon_rrns %>%
	ggplot(aes(x=rank, y=mean_rrns)) + 
	geom_jitter(width=jitter_width, color="gray") +
	geom_segment(data=mean_of_means,
							 aes(x=1:n_ranks-jitter_width, xend=1:n_ranks+jitter_width,
							 		y=mean_mean_rrns, yend=mean_mean_rrns),
						 color="red", group=1, size=2, lineend="round",
						 inherit.aes=FALSE) + 
	theme_classic() +
	labs(x=NULL, 
			 y="Mean number of rrn copies per genome",
			 title="There is wide variation at the species level in the number of rrn copies",
			 subtitle="Each point represents a single taxon within that rank, numbers based on\nan average species copy number") +
	scale_x_discrete(breaks=c("kingdom", "phylum", "class", "order", "family", "genus", "species"),
									 labels=c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species"))
```
